The expected shape of the Milky Way's Dark Matter halo

### 2018-09-24 Paper/paper.tex
table progress

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{subfig}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{subfig}
\usepackage{array}

% Included by user
\usepackage{multirow}
\usepackage{multicol}
\usepackage{blindtext}
\newcolumntype{?}{!{\vrule width 1pt}}

\newenvironment{Table}
   {\par\bigskip\noindent\minipage{\columnwidth}\centering}
   {\endminipage\par\bigskip}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\newpage
%\begin{multicols}{2}
\begin{Table}
%\setlength{\tabcolsep}{3pt}
\begin{tabular}{l|cc|cc|c|c|c}
Refference&$q_{\rho}$&$s_{\rho}$&$q_{\phi}$&$s_{\phi}$&$R$&$\theta$&comment\\ \hline \hline
\citet{Law_and_Majewski_2009}&&&$\mathbf{0.83}$&$\mathbf{0.67}$& $\lesssim 60$kpc&$90^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Mid-axis orientation\\Method: Sagittarius stream}\\
%
\citet{Law_and_Majewski_2010}&&&$\mathbf{0.99}$&$\mathbf{0.72}$& $[20$kpc,$60$kpc$]$&$90^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Mid-axis orientation \\ Method: Sagittarius stream}\\
%
\citet{Deg_and_Widrow_2013}&$0.72$&$0.28$&$0.82$&$0.40$&$[20$kpc,$60$kpc$]$&$90^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Mid-axis orientation\\ Method: Sagittarius stream}\\
%
\citet{Olling_and_Merrifield_2000}&$\mathbf{1.00}$&$\mathbf{0.80}$&&&$\simeq 8$kpc&$0^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Method: Stellar dynamics and HI density.}\\
%
\citet{Bovy_et_el._2016}&$\mathbf{0.95}$&$\mathbf{0.95}$&&&$\lesssim 20$kpc&$90^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Method: Stellar streams}\\
%
\citet{Loebman_et_al._2012}&$\mathbf{1.00}$&$\mathbf{0.47}$&&&$\sim 20$kpc &$0^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Method: SDSS statistics}\\
%
\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&&&$\mathbf{1.00}$&$\mathbf{0.90}$&$\lesssim 10$kpc&$0^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Method: Sagittarius stream \& LMC }\\
&&&$\mathbf{0.90}$&$\mathbf{0.80}$&$\gtrsim 10$kpc&$90^{\circ}$&\multicolumn{1}{p{4.5cm}}{\raggedright Mid-axis orientation on the outside. }\\
\end{tabular}
\end{Table}
%\end{multicols}
